---
title: "Measles_Data_Extraction"
format: html
editor: visual
---

```{r}
library(rvest)
library(dplyr)
library(janitor)
```

First we scrape the data from the CDC website on vaccination and exemption rates.

```{r}
url <- "https://www.cdc.gov/mmwr/volumes/73/wr/mm7341a3.htm"


tables <- read_html(url) |>
  html_table(fill = TRUE)

tbl1 <- tables[[1]] |>
  clean_names()
```

The data needs some cleaning. I only want a couple of the columns, and some of the rows are summary information that I do not want. Also, the columns I am keeping have some other characters in them that I do not want.

```{r}
mmr <- tbl1[5:57,] |>
  select(
  state = jurisdiction,
  mmr_vaccinated = percentage_2, exempt_rate=percentage_7) |>
  mutate(state=gsub("[^A-Za-z ]", "", state))|>
  mutate(mmr_vaccinated=as.numeric(gsub("[^0-9.]","", mmr_vaccinated))) |>
  mutate(exempt_rate=as.numeric(gsub("[^0-9.]","", exempt_rate))) |>
  mutate(state = if_else(state == "District of Columbia","D.C.",state)) |>
  mutate(state = if_else(state == "New York including NYC","New York",state)) |>
  mutate(state = if_else(state == "Texas including Houston","Texas",state)) |>
  mutate(state=trimws(state))



```

Next I will get the data on types of exemptions.

```{r}
url2 <- "https://www.ncsl.org/health/state-non-medical-exemptions-from-school-immunization-requirements"

tables <- read_html(url2) |>
  html_table(fill = TRUE)

tbl2 <- tables[[1]] |>
  clean_names()
```

Clean up this data frame:

```{r}
names(tbl2)

```

```{r}
state_exemptions<-tbl2 |>
  select(state, personal_exemption, religious_exemption) |>
  mutate(any_exemption=ifelse(personal_exemption=="Yes"|religious_exemption=="Yes", "Yes", "No")) |>
  mutate(state=trimws(state))
```

Lastly, we get the number of cases.

```{r}
cases<-read_csv("MeaslesCasesMap.csv")

names(cases)
```

```{r}

library(readr)

cases<-read_csv("MeaslesCasesMap.csv") |>
  mutate(state=Location) |>
  mutate(cases_2025=`2025`) |>
  select(state, cases_2025)|>
  mutate(state = if_else(state == "District of Columbia",
      "D.C.",state))
  
```

Now we join all of the files.

```{r}
measles_data <- left_join(
  state_exemptions,
  mmr,
  by = "state"
)

measles_data <- left_join(
  measles_data,
  cases,
  by = "state"
)
```

Now I'll save the dataframe as a csv to share:

```{r}
write_csv(measles_data, "measles_data.csv")
```
